Turbulence in compact to giant H~II regions

### 2023-04-26 strucfunc_paper.tex
Rewrite description of 3D to 2D mapping
Mention the delta kappa complications

To characterize the impact of the finite map size
and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of
the structure function parameters, such as
the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
The synthetic velocity maps are created using a modified version of the \NEW{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
which creates a \NEW{three-dimensional} fractional Brownian Motion field
\citep{Miville-Deschenes:2003a}
based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
where \NEW{\(n = m + 3\)} and with random phases. 
Our modification multiplies the energy spectrum by a
low-wavenumber exponential taper:
\(e^{-1 / 2 \pi r_0 k}\).
As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
and the resulting structure function closely approximates our model form
(section~\ref{sec:methods-apply}).

@@

For the emissivity field, we assume a log-normal distribution
with RMS fractional width
\(\shortsig{E} = 1.0\) that is typical of our sources
(see footnote~\ref{fn:brightness-fluctuations} and Figure~\ref{fig:brightness-pdfs} above).
We further assume that there is no correlation between the emissivity
and velocity fluctuations and that their spatial correlation length
and power law indices are equal.\footnote{%
  We have investigated departures from these assumptions and found that they
  make very little difference to the results.
}
\stopNEW

@@

We find that the following simple analytic function reproduces
these results to within better than 10\%:
%\begin{equation}\label{eq:seeingemp2}
%S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
%\end{equation}
\begin{equation}\label{eq:seeingemp2}
  \startNEW
  S(r; s_0, r_0) = 
  \left [
    \left (1+a_1\frac{s_0}{r_0} \right) 
    \left(1+ \left (a_2 \frac{ s_0}{r} \right) ^{a_3} \right)
  \right ]^{-1} ,
  \stopNEW
\end{equation}
which is shown by dashed lines in \NEW{Figure \ref{fig:seeing-reduction}b}.
\NEW{%
  The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
  are found to depend slightly on the power law slope \(m\)
  and the magnitude of the emissivity fluctuations \(\shortsig{E}\).
  We adopt the compromise values \(a_1 = 1.25\),
  \(a_2 = 2.6\), and \(a_3 = 1.5\), which fit the numerical results to
  within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
The optimum value of the index \(a\) in this equation varies slightly
with the power law slope \(m\) of the true structure function,
but a compromise value of \(a = 0.75\) works tolerably well for \(m = 0.7\) to \(1.3\).
We therefore use this equation to represent the seeing
in our structure function fits (section~\ref{sec:results}),
with \(s_0\) as an additional free parameter for the models.

>>>>

To characterize the impact of the finite map size
and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of
the structure function parameters, such as
the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
The synthetic velocity maps are created using a modified version of the \NEW{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
which creates a \NEW{three-dimensional} fractional Brownian Motion field
\citep{Miville-Deschenes:2003a}
based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
and with random phases. 
Our modification multiplies the energy spectrum by a
low-wavenumber exponential taper:
\(e^{-1 / 2 \pi r_0 k}\).
As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
and the resulting structure function closely approximates our model form
(section~\ref{sec:methods-apply}).

@@

For the emissivity field, we assume a log-normal distribution
with RMS fractional width
\(\shortsig{E} = 1.0\), which is typical of our sources
(see footnote~\ref{fn:brightness-fluctuations} and Figure~\ref{fig:brightness-pdfs} above).
We further assume that there is no correlation between the emissivity
and velocity fluctuations and that their spatial correlation length
and power law indices are equal.\footnote{%
  \startNEW
  We have investigated departures from these assumptions and found that they
  make very little difference to the results.
  In particular, we have varied \(\shortsig{E}\) between
  0.0 (constant emissivity) and 2.0 (very strong fluctuations,
  as seen in 30~Doradus), and found that the fitting parameters
  for the effects of seeing (see below) change by less than 20\%
  \stopNEW
}

The 3-dimensional 2nd-order structure function slope is related to the power law index as \(m\DDD = n - 3\), but the slope, \(m\), of the 2-dimensional velocity
structure function depends not only on velocity power law index, but also on the magnitude and power law index of the emissivity fluctuations via the quantity
\(\delta\kappa\), with the relation being \(m = n - 2 + \delta\kappa\)
(see section \ref{sec:constancy-power-law}).
\citet{Brunt:2004a} found that \(\delta\kappa\) is a function of the Mach number for
hydrodynamic turbulent box simulations, but we are unaware of any analytic prescription that would allow us to calculate \(\delta\kappa\) for
the fractional Brownian motion models that we use here. 
We therefore adopt an empirical approach by varying \(n\) until the
resultant structure function slope matches a particular value in the
range \(m = 0.8 \to 1.2\)
that encompasses our observational results. 
At each step, we estimate \(m\) by fitting our idealized model structure function
(equation~\eqref{eq:model-strucfunc-ideal}, without the seeing and noise terms)
to the structure function of the simulated velocity map.
In the case of a uniform emissivity field (\(\shortsig{E} = 0\)),
we find \(\delta\kappa \approx 0\),
which is maximal projection smoothing, exactly as expected for a case that
mimics incompressible turbulence.
As the amplitude of the emissivity fluctuations increase,
we find that \(\delta\kappa\) becomes increasingly negative,
with \(\delta\kappa \approx -0.3\) for \(\shortsig{E} = 1\) (the case that we present here)
and \(\delta\kappa \approx -0.55\) for \(\shortsig{E} = 2\).
This is qualitatively consistent with the results in
Figure~12a of \citet{Brunt:2004a}, although a quantitative
comparison is hard to make, since they are not holding \(m\) constant
in the way we do here. 
\stopNEW

@@

We find that the following simple analytic function reproduces
these results to within better than 10\%:
%\begin{equation}\label{eq:seeingemp2}
%S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
%\end{equation}
\begin{equation}\label{eq:seeingemp2}
  \startNEW
  S(r; s_0, r_0) = 
  \left [
    \left (1+a_1\frac{s_0}{r_0} \right) 
    \left(1+ \left (a_2 \frac{ s_0}{r} \right) ^{a_3} \right)
  \right ]^{-1} ,
  \stopNEW
\end{equation}
which is shown by dashed lines in \NEW{Figure \ref{fig:seeing-reduction}b}.
\NEW{%
  The exact values of the constants \(a_1\), \(a_2\), \(a_3\)
  are found to depend slightly on the power law slope \(m\)
  and the magnitude of the emissivity fluctuations \(\shortsig{E}\).
  We adopt the compromise values \(a_1 = 1.25\),
  \(a_2 = 2.6\), and \(a_3 = 1.5\), which fit the numerical results to
  within 20\% for \(0.8 < m < 1.2\) and \(0.5 < \shortsig{E} < 2.0\).}
We therefore use this equation to represent the seeing
in our structure function fits (section~\ref{sec:results}),
with \(s_0\) as an additional free parameter for the models.
